\begin{customexer}{A.18(Proof of Proposition A.17)}\label{exercise_a_18}
  Let $X$ be a topological space and let $S$ be a subspace of $X$.
  \begin{enumerate}[label=(\alph*)]
    \item 
    \item 
    \item 
    \item 
    \item 
    \item 
      If $\mathcal{B}$ is a basis for the topology of $X$, then $\mathcal{B}_S = \{ B \cap S \mid B \in \mathcal{B} \}$ is a basis for the subspace topology on $S$.
    \item 
      If $X$ is Hausdorff, then so is $S$.
    \item 
      If $X$ is first-countable, then so is $S$.
    \item 
      If $X$ is second-countable, then so is $S$.
  \end{enumerate}
\end{customexer}

\begin{proof}
  $ $
  \begin{enumerate}[label=(\alph*)]
    \item 
    \item 
    \item 
    \item 
    \item 
    \item 
      The union of $B \cap S$ is $S$.
      Let $U \cap S$ be an open subset of $S$ where $U$ is open in $X$, and $x \in U \cap S$.
      Then there exists $B \in \mathcal{B}$ such that $x \in B \subset U$ since $\mathcal{B}$ is a basis.
      Therefore, $x \in B \cap S \subset U \cap S$ with $B \cap S \in \mathcal{B}_S$.
    \item 
      Let $x \ne y \in S$.
      There exist two disjoint open sets $U, V$ of $X$ containing $x, y$, respectively.
      Then $U \cap S$ and $V \cap S$ are disjoint open sets of $X$ containing $x, y$, respectively.
    \item 
    \item 
      Let $\mathcal{B}$ be a countable basis of $X$.
      Then $\{ B \cap S \mid B \in \mathcal{B} \}$ is a countable basis of $S$ by (f).
  \end{enumerate}
\end{proof}

\begin{customexer}{A.24(Proof of Proposition A.23)}\label{exercise_a_24}
  Suppose $X_1, \cdots, X_k$ are topological spaces, and let $X_1 \times \cdots \times X_k$ be their product space.
  \begin{enumerate}[label=(\alph*)]
    \item
      CHARACTERISTIC PROPERTY: If $B$ is a topological space, a map $F: B \rightarrow X_1 \times \cdots \times X_k$ is continuous if and only if each of its component functions $F_i = \pi_i \circ F: B \rightarrow X_i$ is continuous.
  \end{enumerate}
\end{customexer}

\begin{proof}
  $ $
  \begin{enumerate}[label=(\alph*)]
    \item
      Suppose $F$ is continuous.
      Since $\pi_i$ is continuous by (c) and the composition of continuous functions is continuous, $\pi_1 \circ F$ is continuous.
      Suppose each component function is continuous.
      Let $B_1 \times \cdots \times B_k$ be a basis element of $X_1 \times \cdots \times X_k$.
      \begin{align*}
        F^{-1}(B_1 \times \cdots \times B_k)
          &= F^{-1}(\cap_{i=1}^{k} \pi_i^{-1}(B_1 \times \cdots \times B_k)) \\
          &= \cap_{i=1}^{k} F^{-1}(\pi_i^{-1}(B_1 \times \cdots \times B_k)) \\
          &= \cap_{i=1}^{k} (\pi_i \circ F)^{-1}(B_1 \times \cdots \times B_k).
      \end{align*}
      Since the intersection of finitely many open sets is open, $F$ is continuous.
  \end{enumerate}
\end{proof}
